---
title: "Geographic pair matching in large-scale cluster randomized trials"
subtitle: "Make overview maps"
author: "Ben Arnold ben.arnold@ucsf.edu"
date: "updated `r Sys.time()`"
output:
  html_document:
    highlight: default
    theme: default
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

# Summary

Make overview maps of the WASH Benefits Bangladesh and Kenya trials. Highlight specific blocks for a didactic figure to illustrate the geographically pair-matched design.

```{r preamble, message = FALSE}
library(here)
here()
#----------------------------
# source the config file
#----------------------------
source(here("R","washb-geopair-Config.R"))

#----------------------------
# Box data file paths
#----------------------------
Box_data_directory    <- "~/Library/CloudStorage/Box-Box/washb-geopair/data/final/"
Box_geodata_directory <- "~/Library/CloudStorage/Box-Box/washb-geopair/data/geodata/"


```


# Process GPS data

These data are generated as part of the WASH Benefits analysis of the efficiency of geographic pair matching

```{r load data}
#----------------------------------
# Load Bangladesh + Kenya GPS data
# and cluster-level means
#----------------------------------
gps_b <- read_rds(file=here(Box_data_directory,"bangl_analysis_gps.rds"))
gps_k <- read_rds(file=here(Box_data_directory,"kenya_analysis_gps.rds"))
dcl <- read_rds(file=here("output","washb_pair_level_summary_estimates.rds"))


#----------------------------------
# Load the Bangladesh and Kenya
# administrative shapefiles
#----------------------------------
admin_b <- st_read(paste0(Box_geodata_directory,"bgd_adm_bbs_20201113_SHP"),layer = "bgd_admbnda_adm3_bbs_20201113")
admin_k <- st_read(paste0(Box_geodata_directory,"ken_adm_iebc_20191031_shp"),layer = "ken_admbnda_adm2_iebc_20191031")

```

# Geodata processing

```{r geodata cleaning}
# there are a small number of clusters (n=4) in Kenya 
# that seem to be geolocated just over the line 
# into a new sub-county. By hand, recode the 
# administrative information for these clusters 
# to be the same as those for the other clusters 
# in the same randomization block.
gps_k <- gps_k %>%
  mutate(
    
    ADM2_PCODE = ifelse(ADM2_PCODE=="KE037202" & block==3,"KE037205",ADM2_PCODE),
    ADM2_EN = ifelse(ADM2_PCODE=="KE037202" & block==3,"Mumias East",ADM2_EN),
    
    ADM2_PCODE = ifelse(ADM2_PCODE=="KE039220" & block==6,"KE039219",ADM2_PCODE),
    ADM2_EN = ifelse(ADM2_PCODE=="KE039220" & block==6,"Bumula",ADM2_EN),
    
    ADM2_PCODE = ifelse(ADM2_PCODE=="KE042239" & block==61,"KE038214",ADM2_PCODE),
    ADM2_EN = ifelse(ADM2_PCODE=="KE042239" & block==61,"Luanda",ADM2_EN),
    
    ADM2_PCODE = ifelse(ADM2_PCODE=="KE041235" & block==61,"KE038214",ADM2_PCODE),
    ADM2_EN = ifelse(ADM2_PCODE=="KE041235" & block==61,"Luanda",ADM2_EN)
  )


```

```{r geodata processing}
#----------------------------------
# subset the overall GPS data
# to just control and nutrition
# containing clusters for convenience
#
# in Kenya, limit to the 72
# complete blocks for C+N
#----------------------------------
gps_b_c <- gps_b %>%
  filter(tr == "Control")
gps_b_n <- gps_b %>%
  filter(tr %in% c("Nutrition","Nutrition + WSH"))

gps_k_c <- gps_k %>%
  filter(tr == "Control") %>%
  filter(!block %in% c(11,13,20,23,30,33,37,40,49,51,54,56,65,72,80,84,85))
gps_k_n <- gps_k %>%
  filter(tr %in% c("Nutrition","Nutrition + WSH")) %>%
  filter(!block %in% c(11,13,20,23,30,33,37,40,49,51,54,56,65,72,80,84,85))

#---------------------------
# register Bangladesh data
# as an sf object
#---------------------------
sfgps_b <- gps_b %>% 
  st_as_sf(coords = c("lon","lat")) %>%
  st_set_crs(4326)

#---------------------------
# register Kenya data
# as an sf object
#---------------------------
sfgps_k <- gps_k %>% 
  st_as_sf(coords = c("lon","lat")) %>%
  st_set_crs(4326)


#---------------------------
# subset the Bangladesh
# Upazila boundaries to just
# those that intersect study
# clusters
#---------------------------
# this function sums up the number 
# of clusters in the bangladesh subdistrict (upazila) polygons
# admin_b_study_int <- apply(st_intersects(admin_b, sfgps_b, sparse = FALSE),1,function(x) sum(ifelse(x==TRUE,1,0)))

# easlier: just do it with a merge using admin codes 
# that are joined to the GPS data in an earlier step, using a spatial join
admin_b_study <- admin_b %>%
  filter(ADM3_PCODE %in% gps_b$ADM3_PCODE)

#---------------------------
# subset the Kenya
# sub-county boundaries to just
# those that intersect study
# clusters
#---------------------------
admin_k_study <- admin_k %>%
  filter(ADM2_PCODE %in% gps_k$ADM2_PCODE)

```


# Bangladesh clusters

```{r bangladesh single block highlight}
#---------------------------------------
# identify a single block of clusters 
# to use as an example in the figure
# block 11 is on the margin and compact
# so used for an example
#---------------------------------------
single_block_id <- 11
gps_b_single_cl <- gps_b %>%
  filter(block == single_block_id)
#---------------------------
# Identify the convex hull
# around the clusters in the
# block and make a polygon
# for mapping
#---------------------------
single_block_xycoords <- as.matrix(gps_b_single_cl[,c('lon','lat')])

single_block_xychull <- single_block_xycoords[chull(single_block_xycoords),]
single_block_xypoly <- st_polygon(list(rbind(single_block_xychull,single_block_xychull[1,]))) %>%
  st_sfc() %>% st_sf() %>% st_set_crs(4326)
```

```{r map Bangladesh clusters, out.width = "100%"}

xlon <- median(gps_b$lon)
ylat <- median(gps_b$lat)

# make the map
map_b <- leaflet(width = "100%", 
                 options = leafletOptions(zoomControl = TRUE,
                                 zoomSnap = 0.1,
                                 zoomDelta = 0.1)
                 ) %>% 
  addProviderTiles(provider = providers$CartoDB.Positron ,options=providerTileOptions(opacity=1)) %>%
  # addProviderTiles("Stamen.TerrainBackground",options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 8.5) %>%
  # plot Upazila (subdistrict) boundaries
  addPolygons(data = admin_b_study, fillOpacity = 0, color = "#000000", weight=1) %>%
  addCircleMarkers(data = gps_b,
                   lng = ~ lon, lat = ~ lat,
                   radius = 1.5,
                   color = ~ "gray40", fill = ~ "gray40",  weight=1, opacity = 1, fillOpacity = 1,
                   # pop ups with block IDs.
                   popup=paste("Block: ", gps_b$block)
              ) %>%
   # addCircleMarkers(data = gps_b %>% filter(block==single_block_id),
   #                 lng = ~ lon, lat = ~ lat,
   #                 # radius = markerscale*sqrt((dvil3_2014$sea_prev*100)/pi),
   #                 radius = 1,
   #                 color = ~ nytpal[7], fill = ~ nytpal[7],  weight=1, opacity = 1, fillOpacity = 1,
   #                 # pop ups with block IDs.
   #                 popup=paste("Block: ", gps_b$block)
   #            ) %>%
  # addPolygons(data = single_block_xypoly,
  #             # lng = ~ lon, lat = ~ lat,
  #             color = "black",weight=1,fill = FALSE, fillOpacity = 0) %>%

  # add scale bar and legends
  addScaleBar(position="bottomright",options=scaleBarOptions(imperial = FALSE))


map_b


```


```{r map Bangladesh single block, out.width = "100%"}
xlon <- median(gps_b$lon[gps_b$block==single_block_id])
ylat <- median(gps_b$lat[gps_b$block==single_block_id])

# make the map
map_b_single_cl <- leaflet(width = "100%", 
                 options = leafletOptions(zoomControl = TRUE,
                                 zoomSnap = 0.25,
                                 zoomDelta = 0.25)
                 ) %>% 
  # remove labels in the base tile to protect confidentiality
  addProviderTiles(provider = providers$CartoDB.PositronNoLabels,options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 12) %>%
  
  # add convex hull of the highlighted block
  # (not used)
  # addPolygons(data = single_block_xypoly,
  #             # lng = ~ lon, lat = ~ lat,
  #             color = "black",weight=1,fill = FALSE, fillOpacity = 0) %>%

  # plot control clusters
   addCircleMarkers(data = gps_b %>% filter(block==single_block_id & tr == "Control"),
                   lng = ~ lon, lat = ~ lat,
                   # radius = markerscale*sqrt((dvil3_2014$sea_prev*100)/pi),
                   radius = 7,
                   color = ~ "black", fillColor = cbpal[5],   weight=1, opacity = 1, fillOpacity = 1
              ) %>%
  # plot nutrition clusters
  addCircleMarkers(data = gps_b %>% filter(block==single_block_id & tr %in% c("Nutrition","Nutrition + WSH")),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = ~ cbpal[4], fillColor = cbpal[4],
                   weight=1, opacity =1, fillOpacity = 1
              ) %>%
  # plot remaining clusters
  addCircleMarkers(data = gps_b %>% filter(block==single_block_id & !tr %in% c("Control","Nutrition","Nutrition + WSH")),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = FALSE,  
                   weight=1, opacity = 1, fillOpacity = 1,
                   popup=paste("Block: ", gps_b$block[gps_b$block==single_block_id])
              ) %>%
  # plot all other clusters, not in the highlighted block
  addCircleMarkers(data = gps_b %>% filter(block!=single_block_id),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = "black",  
                   weight=1, opacity = 0.1, fillOpacity = 0.2, 
                   popup=paste("Block: ", gps_b$block[gps_b$block!=single_block_id])
              ) %>%
  
  # add scale bar and legends
  addScaleBar(position="bottomright",options=scaleBarOptions(imperial = FALSE))


map_b_single_cl


```

# Kenya clusters

```{r kenya single block highlight}
#---------------------------------------
# identify a single block of clusters 
# to use as an example in the figure
# block 66 is on the margin and compact
# so used for an example
#---------------------------------------
single_block_id_k <- 66
gps_k_single_cl <- gps_k %>%
  filter(block == single_block_id_k)
#---------------------------
# Identify the convex hull
# around the clusters in the
# block and make a polygon
# for mapping
#---------------------------
single_block_xycoords <- as.matrix(gps_b_single_cl[,c('lon','lat')])

single_block_xychull <- single_block_xycoords[chull(single_block_xycoords),]
single_block_xypoly <- st_polygon(list(rbind(single_block_xychull,single_block_xychull[1,]))) %>%
  st_sfc() %>% st_sf() %>% st_set_crs(4326)
```

```{r map Kenya clusters, out.width = "100%"}

xlon <- median(gps_k$lon)
ylat <- median(gps_k$lat)

# make the map
map_k <- leaflet(width = "100%", 
                 options = leafletOptions(zoomControl = TRUE,
                                 zoomSnap = 0.25,
                                 zoomDelta = 0.25)
                 ) %>% 
  addProviderTiles("CartoDB.Positron",options=providerTileOptions(opacity=1)) %>%
  # addProviderTiles("Stamen.TerrainBackground",options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 9) %>%
    # plot Sub-County boundaries (Admin level 2)
  addPolygons(data = admin_k_study, fillOpacity = 0, color = "#000000", weight=1) %>%
  addCircleMarkers(data = gps_k,
                   lng = ~ lon, lat = ~ lat,
                   radius = 1.5,
                   color = ~ "gray40", fill = ~ "gray40",  weight=1, opacity = 1, fillOpacity = 1,
                   # pop ups with block IDs.
                   popup=paste("Block: ", gps_k$block)
              ) %>%
  
  # add scale bar and legends
  addScaleBar(position="bottomright",options=scaleBarOptions(imperial = FALSE))


map_k


```


```{r map Kenya single block, out.width = "100%"}
xlon <- median(gps_k$lon[gps_b$block==single_block_id_k])
ylat <- median(gps_k$lat[gps_b$block==single_block_id_k])

# make the map
map_k_single_cl <- leaflet(width = "100%", 
                 options = leafletOptions(zoomControl = TRUE,
                                 zoomSnap = 0.25,
                                 zoomDelta = 0.25)
                 ) %>% 
  # remove labels in the base tile to protect confidentiality
  addProviderTiles(provider = providers$CartoDB.PositronNoLabels,options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 12) %>%
  
  # add convex hull of the highlighted block
  # (not used)
  # addPolygons(data = single_block_xypoly,
  #             # lng = ~ lon, lat = ~ lat,
  #             color = "black",weight=1,fill = FALSE, fillOpacity = 0) %>%

  # plot control clusters
   addCircleMarkers(data = gps_k %>% filter(block==single_block_id_k & tr == "Control"),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fillColor = cbpal[5],   weight=1, opacity = 1, fillOpacity = 1
              ) %>%
  # plot nutrition clusters
  addCircleMarkers(data = gps_k %>% filter(block==single_block_id_k & tr %in% c("Nutrition","Nutrition + WSH")),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = ~ cbpal[4], fillColor = cbpal[4],
                   weight=1, opacity =1, fillOpacity = 1
              ) %>%
  # plot remaining clusters
  addCircleMarkers(data = gps_k %>% filter(block==single_block_id_k & !tr %in% c("Control","Nutrition","Nutrition + WSH")),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = FALSE,  
                   weight=1, opacity = 1, fillOpacity = 1,
                   popup=paste("Block: ", gps_b$block[gps_b$block==single_block_id_k])
              ) %>%
  # plot all other clusters, not in the highlighted block
  addCircleMarkers(data = gps_k %>% filter(block!=single_block_id_k),
                   lng = ~ lon, lat = ~ lat,
                   radius = 7,
                   color = ~ "black", fill = "black",  
                   weight=1, opacity = 0.1, fillOpacity = 0.2, 
                   popup=paste("Block: ", gps_b$block[gps_b$block!=single_block_id_k])
              ) %>%
  
  # add scale bar and legends
  addScaleBar(position="bottomright",options=scaleBarOptions(imperial = FALSE))


map_k_single_cl


```


# Session Info
```{r session info}
sessionInfo()
```
