---
title: "Relative efficiency of geographic pair matching in the WASH Benefits trials"
subtitle: "Estimate outcome ICCs"
author: "Ben Arnold ben.arnold@ucsf.edu"
date: "updated: `r Sys.time()`"
output: 
  html_document:
    theme: default
    highlight: haddock
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
---

# Summary

Summary here: **TBD**

Details of original citations and data sources here: **TBD**


# Preamble

```{r preamble}
library(here)
here()
#----------------------------
# source the config file
#----------------------------
source(here("R","washb-geopair-Config.R"))

```



# Bangladesh

## Data prep

```{r load bangladesh data}
#-------------------------------
# load the formatted analysis
# data created by
# washb-geopair-data-processing.R
#-------------------------------

# anthropometry data
danth <- read_rds(here("data","bangl_analysis_anthro.rds")) %>%
  mutate(blockf = factor(block))

# diarrhea data
ddiar <- read_rds(here("data","bangl_analysis_diar.rds")) %>%
  mutate(blockf = factor(block))

# giardia data
dpara <- read_rds(here("data","bangl_analysis_parasite.rds")) %>%
  mutate(blockf = factor(block))

```

## Pairwise ICC

Estimate outcome ICC within each pair among the control arm observations.

```{r bangladesh pairwise ICC, warning = FALSE, error = FALSE}

set.seed(9124)

#-------------------------------
# Pair-wise (block level) ICC
# anthropometry outcomes
#-------------------------------
danth_control <- danth %>%
  filter(tr == "Control")
icc_laz <- rptGaussian(laz ~ 1 + (1|blockf), grname = "blockf", data = danth_control, nboot = 1000)
icc_waz <- rptGaussian(waz ~ 1 + (1|blockf), grname = "blockf", data = danth_control, nboot = 1000)
icc_whz <- rptGaussian(whz ~ 1 + (1|blockf), grname = "blockf", data = danth_control, nboot = 1000)
icc_hcz <- rptGaussian(hcz ~ 1 + (1|blockf), grname = "blockf", data = danth_control, nboot = 1000)

#-------------------------------
# Pair-wise (block level) ICC
# Diarrhea
#-------------------------------
ddiar_control <- ddiar %>%
  filter(tr == "Control")
icc_diar <- rptBinary(diar7d ~ 1 + (1|blockf), grname = "blockf", data=ddiar_control, nboot = 1000)

#-------------------------------
# Pair-wise (block level) ICC
# Giardia, Ascaris, Trichuris, Hookworm
#-------------------------------
dpara_control <- dpara %>%
  filter(tr == "Control")
icc_giar <- rptBinary(giar ~ 1 + (1|blockf), grname = "blockf", data=dpara_control, nboot = 1000)
icc_al   <- rptBinary(al ~ 1 + (1|blockf), grname = "blockf", data=dpara_control, nboot = 1000)
icc_tt   <- rptBinary(tt ~ 1 + (1|blockf), grname = "blockf", data=dpara_control, nboot = 1000)
icc_hw   <- rptBinary(hw ~ 1 + (1|blockf), grname = "blockf", data=dpara_control, nboot = 1000)


```

```{r bangladesh icc table}
#-------------------------------
# summarize the results 
# in a table
#-------------------------------
iccs <- unlist( c(icc_laz$R,icc_waz$R, icc_whz$R, icc_hcz$R, icc_diar$R[1,1], icc_giar$R[1,1], icc_al$R[1,1], icc_tt$R[1,1], icc_hw$R[1,1]))
icc_lb <- unlist(c(icc_laz$CI_emp[1],icc_waz$CI_emp[1],icc_whz$CI_emp[1],icc_hcz$CI_emp[1],icc_diar$CI_emp[[1]][1], icc_giar$CI_emp[[1]][1], icc_al$CI_emp[[1]][1], icc_tt$CI_emp[[1]][1], icc_hw$CI_emp[[1]][1]))
icc_ub <- unlist(c(icc_laz$CI_emp[2],icc_waz$CI_emp[2],icc_whz$CI_emp[2],icc_hcz$CI_emp[2],icc_diar$CI_emp[[1]][2], icc_giar$CI_emp[[1]][2], icc_al$CI_emp[[1]][2], icc_tt$CI_emp[[1]][2], icc_hw$CI_emp[[1]][2]))
icc_tab <- data.frame(
  outcome = c("LAZ","WAZ","WHZ","HCZ","Diarrhea","Giardia","Ascaris","Trichuris","Hookworm"),
  icc = iccs,
  icc_min95 = icc_lb,
  icc_max95 = icc_ub
) %>%
  mutate(icc_print = paste0(sprintf("%1.2f",icc)," (",sprintf("%1.2f",icc_min95),", ",sprintf("%1.2f",icc_max95),")"))

knitr::kable(icc_tab %>% select(outcome,icc_print),
             col.names = c("Outcome","ICC (95% CI)"),
             caption = "Bangladesh, outcome ICC among control clusters, grouped by geographically matched pairs, bootstrapped 95% confidence interval") %>%
  kable_styling(bootstrap_options = "striped")

```



# Kenya

## Data prep

```{r load Kenya data}
#-------------------------------
# load the formatted analysis
# data created by
# washb-geopair-data-processing.R
#-------------------------------

# anthropometry data
dkanth <- read_rds(here("data","kenya_analysis_anthro.rds")) %>%
  mutate(blockf = factor(block))

# diarrhea data
dkdiar <- read_rds(here("data","kenya_analysis_diar.rds")) %>%
  mutate(blockf = factor(block))

# giardia data
dkpara <- read_rds(here("data","kenya_analysis_parasite.rds")) %>%
  mutate(blockf = factor(block))

```

## Pairwise ICC

Estimate outcome ICC within each pair among the control arm observations.

```{r kenya pairwise ICC, warning = FALSE, error = FALSE}

set.seed(0928)

#-------------------------------
# Pair-wise (block level) ICC
# anthropometry outcomes
#-------------------------------
dkanth_control <- dkanth %>%
  filter(tr == "Control")
kicc_laz <- rptGaussian(haz ~ 1 + (1|blockf), grname = "blockf", data = dkanth_control, nboot = 1000)
kicc_waz <- rptGaussian(waz ~ 1 + (1|blockf), grname = "blockf", data = dkanth_control, nboot = 1000)
kicc_whz <- rptGaussian(whz ~ 1 + (1|blockf), grname = "blockf", data = dkanth_control, nboot = 1000)
kicc_hcz <- rptGaussian(hcz ~ 1 + (1|blockf), grname = "blockf", data = dkanth_control, nboot = 1000)

#-------------------------------
# Pair-wise (block level) ICC
# Diarrhea
#-------------------------------
dkdiar_control <- dkdiar %>%
  filter(tr == "Control")
kicc_diar <- rptBinary(diarr7 ~ 1 + (1|blockf), grname = "blockf", data=dkdiar_control, nboot = 1000)

#-------------------------------
# Pair-wise (block level) ICC
# Giardia, Ascaris, Hookworm
# no analysis for Trichuris in Kenya (too rare)
#-------------------------------
dkpara_control <- dkpara %>%
  filter(tr == "Control")
kicc_giar <- rptBinary(giar ~ 1 + (1|blockf), grname = "blockf", data=dkpara_control, nboot = 1000)
kicc_al   <- rptBinary(al ~ 1 + (1|blockf), grname = "blockf", data=dkpara_control, nboot = 1000)
kicc_hw   <- rptBinary(hw ~ 1 + (1|blockf), grname = "blockf", data=dkpara_control, nboot = 1000)


```


```{r kenya icc table}
#-------------------------------
# summarize the results 
# in a table
#-------------------------------
kiccs <- unlist( c(kicc_laz$R,kicc_waz$R, kicc_whz$R, kicc_hcz$R, kicc_diar$R[1,1], kicc_giar$R[1,1], kicc_al$R[1,1], kicc_hw$R[1,1]))
kicc_lb <- unlist(c(kicc_laz$CI_emp[1],kicc_waz$CI_emp[1],kicc_whz$CI_emp[1],kicc_hcz$CI_emp[1],kicc_diar$CI_emp[[1]][1], kicc_giar$CI_emp[[1]][1], kicc_al$CI_emp[[1]][1], kicc_hw$CI_emp[[1]][1]))
kicc_ub <- unlist(c(kicc_laz$CI_emp[2],kicc_waz$CI_emp[2],kicc_whz$CI_emp[2],kicc_hcz$CI_emp[2],kicc_diar$CI_emp[[1]][2], kicc_giar$CI_emp[[1]][2], kicc_al$CI_emp[[1]][2], kicc_hw$CI_emp[[1]][2]))
kicc_tab <- data.frame(
  outcome = c("LAZ","WAZ","WHZ","HCZ","Diarrhea","Giardia","Ascaris","Hookworm"),
  icc = kiccs,
  icc_min95 = kicc_lb,
  icc_max95 = kicc_ub
) %>%
  mutate(icc_print = paste0(sprintf("%1.2f",icc)," (",sprintf("%1.2f",icc_min95),", ",sprintf("%1.2f",icc_max95),")"))

knitr::kable(kicc_tab %>% select(outcome,icc_print),
             col.names = c("Outcome","ICC (95% CI)"),
             caption = "Kenya, outcome ICC among control clusters, grouped by geographically matched pairs, bootstrapped 95% confidence interval") %>%
  kable_styling(bootstrap_options = "striped")

```



## Save estimates

Save estimates for re-use in final tables or figures
```{r save icc estimates}
icc_tab_all <- icc_tab %>%
  mutate(country = "Bangladesh") %>%
  bind_rows(kicc_tab) %>%
  mutate(country = ifelse(is.na(country),"Kenya",country))

write_csv(icc_tab_all, path = here("data","washb-geopair-icc-estimates.csv") )

```

# Session Info
```{r session info}
sessionInfo()
```


