---
title: "Assessing global clustering in the WASH Benefits trials"
subtitle: " "
author: "Christine Tedijanto christine.tedijanto@ucsf.edu"
date: "updated: `r Sys.time()`"
output: 
  html_document:
    theme: default
    highlight: haddock
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
---

# Summary

In this analysis, we estimate a measure of global spatial clustering (Moran's I) in the control clusters. There is a quick plot to compare the estimates with the predicted relative efficiency for each outcome of interest based on pair-wise correlation.

# Preamble

```{r preamble, message = FALSE}
library(here)
here()

#----------------------------
# source the config file
#----------------------------
source(here("R","washb-geopair-Config.R"))

#----------------------------
# Box data filepath
#----------------------------
Box_data_directory <- "~/Library/CloudStorage/Box-Box/washb-geopair/data/final/"
```

# Data prep

```{r load gps data}
#-------------------------------
# load the formatted gps
# data created by
# washb-geopair-gps-data-processing.R
#-------------------------------

## Bangladesh -----
# Cluster-level GPS locations (centroids of compounds in each cluster)
# NOT PUBLICLY AVAILABLE -- NEED TO USE ACCURATE LON/LAT FOR MAPPING
dbgps <- read_rds(paste0(Box_data_directory,"bangl_analysis_gps.rds")) %>%
  mutate(block = as.character(block),
         blockf = factor(block))

## Kenya -----
# Cluster-level GPS locations (centroids of compounds in each cluster)
# NOT PUBLICLY AVAILABLE -- NEED TO USE ACCURATE LON/LAT FOR MAPPING
dkgps <- read_rds(paste0(Box_data_directory,"kenya_analysis_gps.rds")) %>%
  mutate(block = as.character(block),
         blockf = factor(block))
```

```{r load cluster level means and relative efficiency}
#-------------------------------
# read-in cluster level means and relative efficiency
# these were estimated in the file
# washb-geopair-relative-efficiency.Rmd
#-------------------------------
dcl <- read_rds(here("data", "washb_pair_level_summary_estimates.rds")) 

ate_res <- read_rds(here("data", "washb_ATE_releff_estimates.rds"))
```

```{r make spatial data}
#-------------------------------
# create gps datasets
# with different methods of assigning
# lat/lon to block
#-------------------------------

#-------------------------------
# dataset 1 has all control
# cluster centroids, used for
# geostatistical model smooths
# of the control group outcomes (n=180)
#-------------------------------

dbgps_control <- dbgps %>%
  filter(tr=="Control") %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat)

dkgps_control <- dkgps %>%
  filter(tr %in% c("Control")) %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat)

#-------------------------------
# dataset 2 has all control and
# nutrition cluster centroids,
# used for geostatistical model smooths
# of the control + nutrition group
# outcomes in a joint model (n=360)
#-------------------------------

dbgps_cn <- dbgps %>%
  filter(tr %in% c("Control","Nutrition","Nutrition + WSH")) %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat)

dkgps_cn <- dkgps %>%
  filter(tr %in% c("Control","Nutrition","Nutrition + WSH")) %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat)

#-------------------------------
# dataset 3 has a row for each block
# median of control clusters only (n=90)
#-------------------------------

dbgps_control_med <- dbgps %>%
  filter(tr=="Control") %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat) %>% 
  group_by(block, blockf) %>%
  summarise(lon = median(lon), lat = median(lat),
            .groups = "keep")

dkgps_control_med <- dkgps %>%
  filter(tr %in% c("Control")) %>%
  dplyr::select(clusterid,tr,block,blockf,lon,lat) %>% 
  group_by(block, blockf) %>%
  summarise(lon = median(lon), lat = median(lat),
            .groups = "keep")
```

# Estimate Moran's I

```{r outcome labels and colors}
# keys to facilitate loops and figures
outcome_lab_key <- data.frame(outcome = c("laz", "waz", "whz", "hcz",
                                          "z_easq_com", "z_easq_motor", "z_easq_pers", "z_cdi_comp", "z_cdi_expr",
                                          "diar7d", "giar", "al", "tt", "hw"),
                              outcome_lab = c("length-for-age z", "weight-for-age z", "weight-for-height z", "head circumference z",
                                              "EASQ communication z", "EASQ gross motor z", "EASQ personal-social z",
                                              "CDI comprehension z", "CDI expression z",
                                              "Diarrhea", "Giardia sp.", "Ascaris sp.", "Trichuris sp.", "Hookworm"),
                              outcome_group = c(rep("Child growth", 4),
                                                 rep("Child development", 5),
                                                 rep("Infectious disease", 5)))

outcome_colors <- c("Child development" = "#D9B86A",
                    "Child growth" = "#9B9F7C",
                    "Infectious disease" = "#5986B0")
```

```{r morani data prep}
# create wide dataframe with summarized variables from control clusters for each block
dcl_Y0bar_wide <- dcl %>% 
  remove_rownames() %>%
  left_join(outcome_lab_key, by = "outcome_lab") %>% 
  dplyr::select(country, block, outcome, Y0bar) %>% 
  pivot_wider(id_cols = c("country", "block"),
              names_from = "outcome",
              values_from = "Y0bar") %>%
  # add lon / lat for control clusters only (median across 2 control clusters in each block)
  left_join(bind_rows(dbgps_control_med %>% mutate(country = "Bangladesh"),
                      dkgps_control_med %>% mutate(country = "Kenya")),
            by = c("country", "block"))
```

```{r morani estimation}
## `get_moran`: wrapper around ape::Moran.I -----
## inputs:
# - input_df: dataframe containing coordinates ("lon", "lat") and variable of interest
# - var (character): variable of interest
## outputs:
# - dataframe with morani outputs (observed, expected, sd, p.value), outcome, and country
get_moran <- function(input_df, var){
  
  # use distGeo distance method, which accounts for curved globe surface
  # gives very similar Moran's I results to dist()
  temp_spatial <- input_df %>%
    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
    as("Spatial")
  
  dist_matrix <- sapply(1:nrow(temp_spatial),
                        function(x) geosphere::distGeo(p1 = temp_spatial, p2 = temp_spatial[x,]))

  # take inverse of distances
  dist_matrix_inv <- 1/dist_matrix
  diag(dist_matrix_inv) <- 0
  
  # estimate Moran's I and statistical significance for each outcome variable 
  ret <- ape::Moran.I(input_df %>% pull(get(var)), dist_matrix_inv) %>% 
    as.data.frame() %>%
    rename_all(~paste0("morani_", .)) %>% 
    mutate(outcome = var)
  
  return(ret)
}

## loop outcomes for Bangladesh and Kenya -----
moranib <- lapply(outcome_lab_key$outcome,
                  function(x){
                    get_moran(input_df = dcl_Y0bar_wide %>% filter(country == "Bangladesh"),
                              var = x)}) %>% 
  bind_rows() %>% 
  mutate(country = "Bangladesh")

moranik <- lapply(setdiff(outcome_lab_key$outcome, c("z_cdi_comp", "z_cdi_expr")),
                  function(x){
                    get_moran(input_df = dcl_Y0bar_wide %>% filter(country == "Kenya"),
                              var = x)}) %>% 
  bind_rows() %>% 
  mutate(country = "Kenya")

## join all moran I results -----
morani_res <- moranib %>% 
  bind_rows(moranik) %>% 
  left_join(outcome_lab_key, by = c("outcome")) %>% 
  left_join(ate_res, by = c("outcome_lab", "country"))
```

# Visualize results

```{r plot morani, fig.width = 8, fig.height = 5}
morani_res %>%
  ggplot(aes(y = morani_observed, x = eff_u)) +
  geom_smooth(method = "gam", se=FALSE, color="gray80") +
  # geom_errorbar(aes(x = morani_observed,
  #                   ymin = releff_min95,
  #                   ymax = releff_max95,
  #                   color = outcome_group)) +
    geom_point(aes(fill = outcome_group), pch = 21,
               alpha = 0.8, size = 2) +
  
  scale_color_manual(values = outcome_colors,guide=guide_legend(title="outcome group:")) +
  scale_fill_manual(values = outcome_colors) +
  scale_y_continuous(breaks = seq(0,0.16,by=0.02)) + 
  scale_x_continuous(breaks = seq(1,4,by=0.5)) + 
  coord_cartesian(xlim=c(1,2.5)) +
  labs(y = "global clustering in the control group (Moran's I)", 
       x = expression(paste("predicted relative efficiency of geographic pair-matching, (1-",italic(r),")")^-1)) +
  facet_wrap(.~country, nrow = 1) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size=11),
    panel.grid.minor.y = element_blank()
    )
```

# Save estimates

Save Moran's I estimates for composite plots or tables

```{r save results}
write_csv(morani_res,file=here("data","washb-geopair-morans-I-estimates.csv"))
write_rds(morani_res,file=here("data","washb-geopair-morans-I-estimates.rds"))

```

# Session Info

```{r session info}
sessionInfo()
```

